Differences from our PPoPP Conference Paper \cite{KBP16}

### 2018-09-07 latex/toms/experiments.tex
made axes uniform with toggles for each set of plots

%set which run to plot
\renewcommand{\run}{32}
\renewcommand{\xmax}{4.9}
\subfloat[Low rank $k=32$ \label{fig:accuracylr81k32}]{
\ylabeltrue
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracylr81pksweep.csv}
\renewcommand{\run}{32}
\relerrplot
\end{tikzpicture}
\ylabelfalse
}
\subfloat[Low rank $k=64$ \label{fig:accuracylr81k64}]{
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracylr81pksweep.csv}
\renewcommand{\run}{64}
\relerrplot
\end{tikzpicture}
}
\subfloat[Low rank $k=96$ \label{fig:accuracylr81k96}]{
\ylabeltrue
\widertrue
\legendtrue
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracylr81pksweep.csv}
\renewcommand{\run}{96}
\relerrplot
\end{tikzpicture}
\ylabelfalse
}
\caption{Relative error comparison of \MU, \HALS, \BPP\, \ADMM, \Nestrov on 4D Synthetic Low Rank Tensor of size 129x129x129x129 on 3x3x3x3 Processor Grid.}
\label{fig:convergencelowrank}
\end{figure}

\begin{figure}
%set which run to plot
\renewcommand{\run}{32}
\renewcommand{\xmax}{9.9}
\subfloat[Low rank $k=32$ \label{fig:accuracylr81k32}]{
\ylabeltrue
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracyuni81pksweep.csv}
\renewcommand{\run}{32}
\relerrplot
\end{tikzpicture}
\ylabelfalse
}
\subfloat[Low rank $k=64$ \label{fig:accuracylr81k64}]{
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracyuni81pksweep.csv}
\renewcommand{\run}{64}
\relerrplot
\end{tikzpicture}
}
\subfloat[Low rank $k=96$ \label{fig:accuracylr81k96}]{
\ylabeltrue
\widertrue
\legendtrue
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracyuni81pksweep.csv}
\renewcommand{\run}{96}
\relerrplot
\end{tikzpicture}
\ylabelfalse
}
\caption{Relative error comparison of \MU, \HALS, \BPP\, \ADMM, \Nestrov on 4D Synthetic Uniform Tensor of size 162x162x162x162 on 3x3x3x3 Processor Grid.}
\label{fig:convergenceuniform}
\end{figure}

@@

%set which run to plot
\renewcommand{\numiterations}{29}
\renewcommand{\nogpu}{1}
\renewcommand{\xmax}{128}

\subfloat[CPU \label{fig:cpulr81}]{
\ylabeltrue
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracylr81pksweep.csv}
\renewcommand{\nogpu}{0}
\cpuvsgpuplot
\end{tikzpicture}
\ylabelfalse
}
\subfloat[GPU \label{fig:gpulr81}]{
\widertrue
\legendtrue
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracylr81pksweep.csv}
\renewcommand{\nogpu}{1}
\cpuvsgpuplot
\end{tikzpicture}
}
\caption{Timing comparison of \MU, \HALS, \BPP\, \ADMM, \Nestrov on 4D Synthetic Low Rank Tensor of size 162x162x162x162 on 3x3x3x3 Processor Grid on CPU.}
\label{fig:cpuvsgpulowrank}
\end{figure}

@@

%set which run to plot
\renewcommand{\numiterations}{29}
\renewcommand{\nogpu}{0}
\renewcommand{\xmax}{150}

\subfloat[CPU \label{fig:cpuuni81}]{
\ylabeltrue
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracyuni81pksweep.csv}
\cpuvsgpuplot
\end{tikzpicture}
\ylabelfalse
}
\subfloat[GPU \label{fig:gpuuni81}]{
\widertrue
\legendtrue
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracyuni81pksweep.csv}
\renewcommand{\nogpu}{1}
\cpuvsgpuplot
\end{tikzpicture}
}
\caption{Timing comparison of \MU, \HALS, \BPP\, \ADMM, \Nestrov on 4D Synthetic Uniform Tensor of size 162x162x162x162 on 3x3x3x3 Processor Grid on CPU.}
\label{fig:cpuvsgpuuniform}
\end{figure}

\renewcommand{\numiterations}{29}
\begin{figure}
\subfloat[Uniform \label{fig:lucuni81}]{
\ylabeltrue
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/lucuni81pksweep.csv}
\lucplot
\end{tikzpicture}
\ylabelfalse
}
\subfloat[Low Rank \label{fig:luclr81}]{
\widertrue
\legendtrue
\begin{tikzpicture}
\renewcommand{\datafile}{data/luclr81pksweep.csv}
\renewcommand{\nogpu}{1}
\lucplot
\end{tikzpicture}
}
\caption{LUC comparison of \MU, \HALS, \BPP\, \ADMM, \Nestrov on 4D Synthetic Uniform and Low Rank Tensor of size 162x162x162x162 on 3x3x3x3 Processor Grid on CPU.}
\label{fig:luccomp}
\end{figure}

>>>>

%set which run to plot
\renewcommand{\run}{32}
\renewcommand{\xmax}{4.9}
\renewcommand{\ymin}{0}
\renewcommand{\ymax}{.25}
\subfloat[Low rank $k=32$ \label{fig:accuracylr81k32}]{
\tikzsetnextfilename{accuracylr81k32}
\ylabeltrue
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracylr81pksweep.csv}
\renewcommand{\run}{32}
\relerrplot
\end{tikzpicture}
\ylabelfalse
}
\subfloat[Low rank $k=64$ \label{fig:accuracylr81k64}]{
\tikzsetnextfilename{accuracylr81k64}
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracylr81pksweep.csv}
\renewcommand{\run}{64}
\relerrplot
\end{tikzpicture}
}
\subfloat[Low rank $k=96$ \label{fig:accuracylr81k96}]{
\tikzsetnextfilename{accuracylr81k96}
\ylabeltrue
\widertrue
\legendtrue
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracylr81pksweep.csv}
\renewcommand{\run}{96}
\relerrplot
\end{tikzpicture}
\ylabelfalse
}
\caption{Relative error comparison of \MU, \HALS, \BPP\, \ADMM, \Nestrov\ on 4D Synthetic Low Rank Tensor of size 129x129x129x129 on 3x3x3x3 Processor Grid.}
\label{fig:convergencelowrank}
\end{figure}

\begin{figure}
%set which run to plot
\renewcommand{\run}{32}
\renewcommand{\xmax}{9.9}
\renewcommand{\ymin}{.4}
\renewcommand{\ymax}{.52}
\subfloat[Low rank $k=32$ \label{fig:accuracylr81k32}]{
\tikzsetnextfilename{accuracylr81k32}
\ylabeltrue
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracyuni81pksweep.csv}
\renewcommand{\run}{32}
\relerrplot
\end{tikzpicture}
\ylabelfalse
}
\subfloat[Low rank $k=64$ \label{fig:accuracylr81k64}]{
\tikzsetnextfilename{accuracylr81k64}
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracyuni81pksweep.csv}
\renewcommand{\run}{64}
\relerrplot
\end{tikzpicture}
}
\subfloat[Low rank $k=96$ \label{fig:accuracylr81k96}]{
\tikzsetnextfilename{accuracylr81k96}
\ylabeltrue
\widertrue
\legendtrue
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracyuni81pksweep.csv}
\renewcommand{\run}{96}
\relerrplot
\end{tikzpicture}
\ylabelfalse
}
\caption{Relative error comparison of \MU, \HALS, \BPP\, \ADMM, \Nestrov\ on 4D Synthetic Uniform Tensor of size 162x162x162x162 on 3x3x3x3 Processor Grid.}
\label{fig:convergenceuniform}
\end{figure}

@@

%set which run to plot
\renewcommand{\numiterations}{29}
\renewcommand{\nogpu}{1}
\renewcommand{\xmax}{128}
\renewcommand{\ymax}{12}

\subfloat[CPU \label{fig:cpulr81}]{
\tikzsetnextfilename{cpulr81}
\ylabeltrue
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracylr81pksweep.csv}
\renewcommand{\nogpu}{0}
\cpuvsgpuplot
\end{tikzpicture}
\ylabelfalse
}
\subfloat[GPU \label{fig:gpulr81}]{
\tikzsetnextfilename{gpulr81}
\widertrue
\legendtrue
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracylr81pksweep.csv}
\renewcommand{\nogpu}{1}
\cpuvsgpuplot
\end{tikzpicture}
}
\caption{Timing comparison of \MU, \HALS, \BPP\, \ADMM, \Nestrov\ on 4D Synthetic Low Rank Tensor of size 162x162x162x162 on 3x3x3x3 Processor Grid on CPU.}
\label{fig:cpuvsgpulowrank}
\end{figure}

@@

%set which run to plot
\renewcommand{\numiterations}{29}
\renewcommand{\nogpu}{0}
\renewcommand{\xmax}{125}
\renewcommand{\ymax}{12}

\subfloat[CPU \label{fig:cpuuni81}]{
\tikzsetnextfilename{cpuuni81}
\ylabeltrue
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracyuni81pksweep.csv}
 \cpuvsgpuplot
\end{tikzpicture}
\ylabelfalse
}
\subfloat[GPU \label{fig:gpuuni81}]{
\tikzsetnextfilename{gpuuni81}
\widertrue
\legendtrue
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracyuni81pksweep.csv}
\renewcommand{\nogpu}{1}
\cpuvsgpuplot
\end{tikzpicture}
}
\caption{Timing comparison of \MU, \HALS, \BPP\, \ADMM, \Nestrov\ on 4D Synthetic Uniform Tensor of size 162x162x162x162 on 3x3x3x3 Processor Grid on CPU.}
\label{fig:cpuvsgpuuniform}
\end{figure}

\renewcommand{\numiterations}{29}
\renewcommand{\xmax}{125}
\renewcommand{\ymax}{.05}
\begin{figure}
\subfloat[Uniform \label{fig:lucuni81}]{
\tikzsetnextfilename{lucuni81}
\ylabeltrue
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/lucuni81pksweep.csv}
\lucplot
\end{tikzpicture}
\ylabelfalse
}
\subfloat[Low Rank \label{fig:luclr81}]{
\tikzsetnextfilename{luclr81}
\widertrue
\legendtrue
\begin{tikzpicture}
\renewcommand{\datafile}{data/luclr81pksweep.csv}
\renewcommand{\nogpu}{1}
\lucplot
\end{tikzpicture}
}
\caption{LUC comparison of \MU, \HALS, \BPP\, \ADMM, \Nestrov\ on 4D Synthetic Uniform and Low Rank Tensor of size 162x162x162x162 on 3x3x3x3 Processor Grid on CPU.}
\label{fig:luccomp}
\end{figure}

### 2018-09-07 latex/toms/plots.tex
made axes uniform with toggles for each set of plots

% macros for plotting
\newcommand{\datafile}{}
\newcommand{\alg}{}
\newcommand{\numiterations}{30}
\newcommand{\minvalue}{1}
\newcommand{\run}{16}
\newcommand{\nogpu}{0}
\newcommand{\xmax}{10}

@@

% set options for relative error over time plot
\newcommand{\relerrplotoptions}{
	xlabel=Time (s),
	xmin=0,
	xmax=\xmax,
	domain=0:\xmax,
	\ifylabel
		ylabel=Relative Error,
		ylabel style={yshift=-.3cm},
	\fi
	\ifwider
		width=1.8in, height=2in,
	\else
		width=1.35in, height=2in,
	\fi
	y tick label style={
        /pgf/number format/.cd,
            precision=4,
            % change "directory" back to tikz
                /tikz/.cd,
	},
	legend style={draw=none, cells={align=left}, nodes={scale=0.7}}
}

% plot relative error over time, filtering rows out appropriately
\newcommand{\relerrplot}{
\begin{axis}[\relerrplotoptions]
	\addplot+ [unbounded coords=jump,discard if not={algo}{0},discard if not={k}{\run},discard if not={gpu}{1},green,thick,mark options={solid}] table [x={totaltime}, y={relerr}] {\datafile};
	\addplot+ [unbounded coords=jump,discard if not={algo}{1},discard if not={k}{\run},discard if not={gpu}{1},red,thick,mark options={solid},mark=square*] table [x={totaltime}, y={relerr}] {\datafile};
	\addplot+ [unbounded coords=jump,discard if not={algo}{2},discard if not={k}{\run},discard if not={gpu}{1},blue,thick,mark options={solid},mark=triangle*] table [x={totaltime}, y={relerr}] {\datafile};
		\addplot+ [unbounded coords=jump,discard if not={algo}{4},discard if not={k}{\run},discard if not={gpu}{1},magenta,thick,mark options={solid},mark=diamond*] table [x={totaltime}, y={relerr}] {\datafile};
			\addplot+ [unbounded coords=jump,discard if not={algo}{5},discard if not={k}{\run},discard if not={gpu}{1},black,thick,mark options={solid},mark=pentagon*] table [x={totaltime}, y={relerr}] {\datafile};
	\iflegend
		\legend{MU,HALS,ABPP,ADMM,Nestrov}
	\fi
\end{axis}
}

% set options for relative error over time plot
\newcommand{\cpuvsgpuoptions}{
	xlabel=Low Rank,
	xmin=0,
	xmax=150, 
	domain=0:150,
	\ifylabel
		ylabel=Time(s),
		ylabel style={yshift=-.3cm},
	\fi
	\ifwider
		width=2in, height=2in,
	\else
		width=1.35in, height=2in,
	\fi
	y tick label style={
        /pgf/number format/.cd,
            precision=4,
            % change "directory" back to tikz
                /tikz/.cd,
	},
	legend style={draw=none, cells={align=left}, nodes={scale=0.7}}
}

% plot relative error over time, filtering rows out appropriately
\newcommand{\cpuvsgpuplot}{
\begin{axis}[\cpuvsgpuoptions]
	\addplot+ [discard if not={algo}{0},discard if not={gpu}{\nogpu},discard if not={iter}{\numiterations},green,thick,mark options={solid}] table [x={k}, y={totaltime}] {\datafile};
	\addplot+ [discard if not={algo}{1},discard if not={gpu}{\nogpu},discard if not={iter}{\numiterations},red,thick,mark options={solid},mark=square*] table [x={k}, y={totaltime}] {\datafile};
	\addplot+ [discard if not={algo}{2},discard if not={gpu}{\nogpu},discard if not={iter}{\numiterations},blue,thick,mark options={solid},mark=triangle*] table [x={k}, y={totaltime}] {\datafile};
		\addplot+ [discard if not={algo}{4},discard if not={gpu}{\nogpu},discard if not={iter}{\numiterations},magenta,thick,mark options={solid},mark=diamond*] table [x={k}, y={totaltime}] {\datafile};
			\addplot+ [discard if not={algo}{5},discard if not={gpu}{\nogpu},discard if not={iter}{\numiterations},black,thick,mark options={solid},mark=pentagon*] table [x={k}, y={totaltime}] {\datafile};
	\iflegend
		\legend{MU,HALS,ABPP,ADMM,Nestrov}
	\fi
\end{axis}
}

\newcommand{\lucplot}{
\begin{axis}[\cpuvsgpuoptions]
	\addplot+ [unbounded coords=jump,discard if not={algo}{0},green,thick,mark options={solid}] table [x={k}, y expr=((\thisrow{nnls}/(\minvalue*\numiterations))] {\datafile};
	\addplot+ [unbounded coords=jump,discard if not={algo}{1},red,thick,mark options={solid},mark=square*] table [x={k}, y expr=((\thisrow{nnls}/(\minvalue*\numiterations))] {\datafile};
	\addplot+ [unbounded coords=jump,discard if not={algo}{2},blue,thick,mark options={solid},mark=triangle*] table [x={k}, y expr=((\thisrow{nnls}/(\minvalue*\numiterations))] {\datafile};
		\addplot+ [unbounded coords=jump,discard if not={algo}{4},magenta,thick,mark options={solid},mark=diamond*] table [x={k}, y expr=((\thisrow{nnls}/(\minvalue*\numiterations))] {\datafile};
			\addplot+ [unbounded coords=jump,discard if not={algo}{5},black,thick,mark options={solid},mark=pentagon*] table [x={k}, y expr=((\thisrow{nnls}/(\minvalue*\numiterations))] {\datafile};
	\iflegend
		\legend{MU,HALS,ABPP,ADMM,Nestrov}
	\fi
\end{axis}
}

>>>>

% macros for plotting
\newcommand{\datafile}{}
\newcommand{\alg}{}
\newcommand{\numiterations}{30}
\newcommand{\minvalue}{1}
\newcommand{\run}{16}
\newcommand{\nogpu}{0}
\newcommand{\xmax}{10}
\newcommand{\ymin}{0}
\newcommand{\ymax}{10}

@@

% set options for relative error over time plot
\newcommand{\relerrplotoptions}{
	xlabel=Time (s),
	xmin=0,
	xmax=\xmax,
	%domain=0:\xmax,
	ymin=\ymin,
	ymax=\ymax,
	\ifylabel
		ylabel=Relative Error,
		ylabel style={yshift=-.3cm},
	\fi
	\ifwider
		width=1.8in, height=2in,
	\else
		width=1.35in, height=2in,
	\fi
%	y tick label style={
%        /pgf/number format/.cd,
%            precision=4,
%            % change "directory" back to tikz
%                /tikz/.cd,
%	},
	legend style={draw=none, cells={align=left}, nodes={scale=0.7}}
}

% plot relative error over time, filtering rows out appropriately
\newcommand{\relerrplot}{
\begin{axis}[\relerrplotoptions]
	\addplot+ [unbounded coords=jump,discard if not={algo}{0},discard if not={k}{\run},discard if not={gpu}{1},green,thick,mark options={solid}] table [x={totaltime}, y={relerr}] {\datafile};
	\addplot+ [unbounded coords=jump,discard if not={algo}{1},discard if not={k}{\run},discard if not={gpu}{1},red,thick,mark options={solid},mark=square*] table [x={totaltime}, y={relerr}] {\datafile};
	\addplot+ [unbounded coords=jump,discard if not={algo}{2},discard if not={k}{\run},discard if not={gpu}{1},blue,thick,mark options={solid},mark=triangle*] table [x={totaltime}, y={relerr}] {\datafile};
		\addplot+ [unbounded coords=jump,discard if not={algo}{4},discard if not={k}{\run},discard if not={gpu}{1},magenta,thick,mark options={solid},mark=diamond*] table [x={totaltime}, y={relerr}] {\datafile};
			\addplot+ [unbounded coords=jump,discard if not={algo}{5},discard if not={k}{\run},discard if not={gpu}{1},black,thick,mark options={solid},mark=pentagon*] table [x={totaltime}, y={relerr}] {\datafile};
	\iflegend
		\legend{MU,HALS,ABPP,ADMM,Nesterov}
	\fi
\end{axis}
}

% set options for relative error over time plot
\newcommand{\cpuvsgpuoptions}{
	xlabel=Low Rank,
	xmin=0,
	xmax=\xmax, 
	ymin=0,
	ymax=\ymax,
	\ifylabel
		ylabel=Time(s),
		ylabel style={yshift=-.3cm},
	\fi
	\ifwider
		width=2in, height=2in,
	\else
		width=1.35in, height=2in,
	\fi
	legend style={draw=none, cells={align=left}, nodes={scale=0.7}},
	legend pos={north west}
}

% plot relative error over time, filtering rows out appropriately
\newcommand{\cpuvsgpuplot}{
\begin{axis}[\cpuvsgpuoptions]
	\addplot+ [discard if not={algo}{0},discard if not={gpu}{\nogpu},discard if not={iter}{\numiterations},green,thick,mark options={solid}] table [x={k}, y={totaltime}] {\datafile};
	\addplot+ [discard if not={algo}{1},discard if not={gpu}{\nogpu},discard if not={iter}{\numiterations},red,thick,mark options={solid},mark=square*] table [x={k}, y={totaltime}] {\datafile};
	\addplot+ [discard if not={algo}{2},discard if not={gpu}{\nogpu},discard if not={iter}{\numiterations},blue,thick,mark options={solid},mark=triangle*] table [x={k}, y={totaltime}] {\datafile};
		\addplot+ [discard if not={algo}{4},discard if not={gpu}{\nogpu},discard if not={iter}{\numiterations},magenta,thick,mark options={solid},mark=diamond*] table [x={k}, y={totaltime}] {\datafile};
			\addplot+ [discard if not={algo}{5},discard if not={gpu}{\nogpu},discard if not={iter}{\numiterations},black,thick,mark options={solid},mark=pentagon*] table [x={k}, y={totaltime}] {\datafile};
	\iflegend
		\legend{MU,HALS,ABPP,ADMM,Nesterov}
	\fi
\end{axis}
}

\newcommand{\lucplot}{
\begin{axis}[\cpuvsgpuoptions]
	\addplot+ [unbounded coords=jump,discard if not={algo}{0},green,thick,mark options={solid}] table [x={k}, y expr=((\thisrow{nnls}/(\minvalue*\numiterations))] {\datafile};
	\addplot+ [unbounded coords=jump,discard if not={algo}{1},red,thick,mark options={solid},mark=square*] table [x={k}, y expr=((\thisrow{nnls}/(\minvalue*\numiterations))] {\datafile};
	\addplot+ [unbounded coords=jump,discard if not={algo}{2},blue,thick,mark options={solid},mark=triangle*] table [x={k}, y expr=((\thisrow{nnls}/(\minvalue*\numiterations))] {\datafile};
		\addplot+ [unbounded coords=jump,discard if not={algo}{4},magenta,thick,mark options={solid},mark=diamond*] table [x={k}, y expr=((\thisrow{nnls}/(\minvalue*\numiterations))] {\datafile};
			\addplot+ [unbounded coords=jump,discard if not={algo}{5},black,thick,mark options={solid},mark=pentagon*] table [x={k}, y expr=((\thisrow{nnls}/(\minvalue*\numiterations))] {\datafile};
	\iflegend
		\legend{MU,HALS,ABPP,ADMM,Nesterov}
	\fi
\end{axis}
}
